## Anova Example 1

### Plot the Data

```{r}
suppressMessages(library(ggplot2))
mlb <- read.csv("https://raw.githubusercontent.com/roualdes/data/master/mlb.csv")
p <- ggplot(data=mlb, aes(x=position, y=salary)) +
geom_boxplot() +
theme(axis.text.x=element_text(angle=45, hjust=1))
p
```

### Linear Model

The `lm` function creates a fitted linear model from the
given variables and data set.

The `anova` function performs analysis of variance on the resulting
linear model object

```{r}
model <- lm(salary~position, data=mlb)
model
res <- anova(model)
res
```

```{r}
# Ensure that the position variable is a factor
is.factor(mlb[,"position"])
```

```{r}
alpha <- 0.05

res$"Pr(>F)"[1] < alpha
```

Because p-value is less than $alpha$=`r alpha`, we reject the
null hypothesis.

## Anova Example 2: Carnivora

### Obtain Data

```{r}
suppressMessages({library(ape)
library(dplyr)
library(ggplot2)
data(carnivora)})
```

```{r}
# Filter down to just 5 families

data(carnivora)

# Remove 3 families
carnivs <- filter(carnivora,
!(Family %in% c("Ailuridae",
"Procyonidae",
"Viverridae")))
head(carnivs)

# Run anova
mod <- lm(SB~Family, data=carnivs)
anova(mod)
```

### Plot the Data

```{r}
p <- ggplot(carnivs, aes(Family, SB)) +
geom_point() +
stat_summary(fun=mean, colour="red",
geom="point", size=4) +
labs(y="Brain Weight")
p
```

### Coefficients

Calling the function `coefficients` on the linear model returns
the intercept and $k − 1$ values $\beta_j$

```{r}
coefficients(mod)

# Compare coefficients to group means
carnivs %>%
    group_by(Family) %>%
    summarise(m=mean(SB))

# Retriece fitted values
yhat <- fitted(mod)
head(yhat)
tail(yhat)
```

