```{r}
data(iris)
head(iris)
```

### Testing

```{r}
summary(
  lm(Petal.Width ~ Species + Species:Petal.Length, data = iris)
)

summary(
  lm(Petal.Width ~ Species * Petal.Length, data = iris)
)
```


### Way 1: Categorical * Numerical

```{r}
way1 <- lm(Petal.Width ~ Species * Petal.Length, data = iris)
summary(way1)
```

Notes:
- Gives slope for **baseline** group.
- Adjustment terms to _slope_ and the _intercept_ for the other groups.

### Way 2: Categorical + Numerical + Categorical:Numerical

```{r}
way2 <- lm(Petal.Width ~ Species + Petal.Length + Species:Petal.Length, data = iris)
summary(way2)
```

Notes:
- Exactly the same as way 1


### Way 3: Categorical + Categorical:Numerical

```{r}
way3 <- lm(Petal.Width ~ Species + Species:Petal.Length, data = iris)
summary(way3)
```

Notes:
- Separate slope terms for each category.
- Adjustment terms to intercept but _not_ to slope.
- No initial slope, just absolute slopes


### No Interaction Terms: Categorical + Numerical

- Different lines from previous models
- Different intercepts, but same slope for all 3 lines
- Not the same equations as above

```{r}
way.noint <- lm(Petal.Width ~ Species, data = iris)
summary(way.noint)
```


## Model Selection

```{r}
finches <- read.csv("https://raw.githubusercontent.com/njlytal/MATH314/main/finches.csv")
str(finches)
```

**Goal**: Create a model to predict winglength based on all numerical vars

```{r}
model <- lm(
  winglength ~ taillength +
    beakwidth + beakwidth +
    beakheight + lowerbeaklength +
    upperbeaklength + tarsuslength +
    middletoelength,
  data = finches
)
summary(model)
```

```{r}
model <- lm(
  winglength ~ taillength +
    beakheight,
  data = finches
)
summary(model)
```


